### 2020-10-15 priority-cp.tex
Created compacttheorems environment for compact theorems in sequence.

\subsubsection*{Operational Semantics}
The operational semantics for PCP, given in \cref{fig:pcp-operational-semantics}, is defined as a reduction relation $\pcp{\red}$ on processes (bottom) and uses structural congruence (top). Each of the axioms of structural congruence corresponds to the axiom of the same name for PGV. We write $\pcp{\red^+}$ for the transitive closures, and $\pcp{\tred^\star}$ for the reflexive-transitive closures.\simon{Maybe worth highlighting that it is an internal mobility calculus, for the pi calculus people.}

@@

\subsubsection*{Subject reduction}
Reduction in our version of PCP preserve types. Since our reduction relation is a strict subset of the reduction relation in the original~\cite{dardhagay18}, we defer to their proofs:
\begin{restatablelemma}{lempcpsubjectcongruence}[Subject Congruence, $\pcp{\equiv}$]
  \label{lem:pcp-subject-congruence}
  \hfill\\%newline before theorem statement
  If $\pcp{\seq{P}{\ty{\Gamma}}}$ and $\pcp{\tm{P}\equiv\tm{Q}}$,
  then $\pcp{\seq{Q}{\ty{\Gamma}}}$.
\end{restatablelemma}
\begin{restatabletheorem}{thmpcpsubjectreduction}[Subject Reduction, $\pcp{\red}$]
  \label{thm:pcp-subject-reduction}
  \hfill\\%newline before theorem statement
  If $\pcp{\seq{P}{\ty{\Gamma}}}$ and $\pcp{\tm{P}\red\tm{Q}}$, then $\pcp{\seq{Q}{\ty{\Gamma}}}$.
\end{restatabletheorem}

@@

Recall our implementations of Milner's cyclic scheduler in PCP ($\pcp{\sched}$, \cref{sec:pcp-example}) and PGV ($\pgv{\sched}$, \cref{sec:pgv-example}). The translation of $\pcp{\sched}$ is exactly $\pgv{sched}$ where all processes are child processes.

\subsubsection*{Type preservation}
The translations $\tm{\cpgvC{\cdot}}$ and $\tm{\cpgvM{\cdot}}$ preserve typing along $\ty{\cpgvT{\cdot}}$:\simon{This reads weirdly---what's the intuition?}
\begin{restatablelemma}{lempcptopgvtermspreservation}[Preservation, $\cpgvM{\cdot}$]
  \label{lem:pcp-to-pgv-terms-preservation}
  \hfill\\%newline before theorem statement
  If $\pcp{\seq{P}{\ty{\Gamma}}}$ in PCP,
  then $\pgv{\tseq[\cs{p}]{\ty{\cpgvT{\Gamma}}}{\cpgvM{P}}{\tyunit}}$ in PGV.
\end{restatablelemma}
\begin{proof}
  By induction on the derivation of $\pcp{\seq{P}{\ty{\Gamma}}}$.
  Details in \cref{prf:lem-pcp-to-pgv-terms-preservation}.
\end{proof}
\begin{restatabletheorem}{thmpcptopgvconfspreservation}[Preservation, $\cpgvC{\cdot}$]
  \label{thm:pcp-to-pgv-confs-preservation}
  \hfill\\%newline before theorem statement
  If $\pcp{\seq{P}{\ty{\Gamma}}}$ in PCP,
  then $\pgv{\cseq[\child]{\ty{\cpgvT{\Gamma}}}{\cpgvC{P}}}$ in PGV.
\end{restatabletheorem}
\begin{proof}
  By induction on the derivation of $\pcp{\seq{P}{\ty{\Gamma}}}$.
  Details in \cref{prf:lem-pcp-to-pgv-terms-preservation}.
\end{proof}

\subsubsection*{Operational correspondence}
Finally, we show that PCP and PGV are in operational correspondence along our translation. First, we link our two translations, and show that $\tm{\cpgvM{P}}$ \emph{must} reduce to $\tm{\cpgvC{P}}$, \ie $\tm{\cpgvC{\cdot}}$ is equivalent to translating with $\tm{\cpgvM{\cdot}}$ and performing several reduction steps:
\begin{restatablelemma}{lempcptopgvcpgvMtocpgvC}
  \label{lem:pcp-to-pgv-cpgvM-to-cpgvC}
  For any $\pcp{\tm{P}}$, either:
  \begin{itemize}
  \item $\pgv{\tm{\child\;\cpgvM{P}}=\tm{\cpgvC{P}}}$; or
  \item   $\pgv{\tm{\child\;\cpgvM{P}}\cred^+\tm{\cpgvC{P}}}$, and for any $\pgv{\tm{\conf{C}}}$, if $\pgv{\tm{\child\;\cpgvM{P}}\cred\tm{\conf{C}}}$, then $\pgv{\tm{\conf{C}}\cred^\star\tm{\cpgvC{P}}}$.
  \end{itemize}
\end{restatablelemma}
\begin{proof}
  By induction on the structure of $\pcp{\tm{P}}$.
  Details in \cref{prf:lem-pcp-to-pgv-cpgvM-to-cpgvC}.
\end{proof}

\begin{restatabletheorem}{thmpcptopgvoperationalcorrespondencecompleteness}%
  [Operational Correspondence, Completeness, $\cpgvC{\cdot}$]
  \label{thm:pcp-to-pgv-operational-correspondence-completeness}
  \hfill\\%newline before theorem statement
  If $\pcp{\seq{P}{\ty{\Gamma}}}$ and $\pcp{\tm{P}\red\tm{Q}}$,
  then $\pgv{\tm{\cpgvC{P}}\cred^+\tm{\cpgvC{Q}}}$.
\end{restatabletheorem}
\begin{proof}
  By induction on the derivation of $\pcp{\tm{P}\red\tm{Q}}$.
  We apply \cref{lem:pcp-to-pgv-cpgvM-to-cpgvC} for the cases in which
  the translation switches from $\tm{\cpgvC{\cdot}}$ to $\tm{\cpgvM{\cdot}}$,
  \ie under actions.
  We apply \cref{lem:pcp-to-pgv-confs-operational-correspondence-equiv} for
  \LabTirName{E-LiftSC}. 
  (Details in \cref{prf:thm-pcp-to-pgv-operational-correspondence-completeness}.)
\end{proof}

\begin{restatabletheorem}{thmpcptopgvoperationalcorrespondencesoundness}%
  [Operational Correspondence, Soundness, $\cpgvC{\cdot}$]
  \label{thm:pcp-to-pgv-operational-correspondence-soundness}
  \hfill\\%newline before theorem statement
  If $\pcp{\seq{P}{\ty{\Gamma}}}$ and $\pgv{\tm{\cpgvC{P}}\cred\tm{\conf{C}}}$,
  there exists a $\tm{Q}$ such that $\pcp{\tm{P}\red^+\tm{Q}}$ and $\pgv{\tm{\conf{C}}\cred^\star\tm{\cpgvC{Q}}}$
\end{restatabletheorem}
\begin{proof}
  By induction on the derivation of $\pgv{\tm{\cpgvC{P}}\cred\tm{\conf{C}}}$.\simon{Surprising that you can get it by the derivation of the reduction relation---normally, 'soundness' would be proved by shunting into a canonical form and then proceeding by induction the structure of the term / induction on typing derivations.}
  Details in \cref{prf:thm-pcp-to-pgv-operational-correspondence-soundness}.
\end{proof}

>>>>

\subsubsection*{Operational Semantics}
The operational semantics for PCP, given in \cref{fig:pcp-operational-semantics}, is defined as a reduction relation $\pcp{\red}$ on processes (bottom) and uses structural congruence (top). Each of the axioms of structural congruence corresponds to the axiom of the same name for PGV. We write $\pcp{\red^+}$ for the transitive closures, and $\pcp{\red^\star}$ for the reflexive-transitive closures.\simon{Maybe worth highlighting that it is an internal mobility calculus, for the pi calculus people.}

@@

\subsubsection*{Subject reduction}
Reduction in our version of PCP preserve types. Since our reduction relation is a strict subset of the reduction relation in the original~\cite{dardhagay18}, we defer to their proofs:
\begin{compacttheorems}
  \begin{restatablelemma}{lempcpsubjectcongruence}[Subject Congruence, $\pcp{\equiv}$]
    \label{lem:pcp-subject-congruence}
    \hfill\\%newline before theorem statement
    If $\pcp{\seq{P}{\ty{\Gamma}}}$ and $\pcp{\tm{P}\equiv\tm{Q}}$,
    then $\pcp{\seq{Q}{\ty{\Gamma}}}$.
  \end{restatablelemma}
  \begin{restatabletheorem}{thmpcpsubjectreduction}[Subject Reduction, $\pcp{\red}$]
    \label{thm:pcp-subject-reduction}
    \hfill\\%newline before theorem statement
    If $\pcp{\seq{P}{\ty{\Gamma}}}$ and $\pcp{\tm{P}\red\tm{Q}}$, then $\pcp{\seq{Q}{\ty{\Gamma}}}$.
  \end{restatabletheorem}
\end{compacttheorems}

@@

Recall our implementations of Milner's cyclic scheduler in PCP ($\pcp{\tm{\sched}}$, \cref{sec:pcp-example}) and PGV ($\pgv{\tm{\sched}}$, \cref{sec:pgv-example}). The translation of $\pcp{\tm{\sched}}$ is exactly $\pgv{\tm{\sched}}$ where all processes are child processes.

\subsubsection*{Type preservation}
The translations $\tm{\cpgvC{\cdot}}$ and $\tm{\cpgvM{\cdot}}$ are preserve typing. The proofs are standard inductions. The details can be found in~\cref{prf:lem-pcp-to-pgv-terms-preservation,prf:lem-pcp-to-pgv-terms-preservation}:
\begin{compacttheorems}
  \begin{restatablelemma}{lempcptopgvtermspreservation}[Preservation, ${\tm{\cpgvM{\cdot}}}$]
    \label{lem:pcp-to-pgv-terms-preservation}
    If $\pcp{\seq{P}{\ty{\Gamma}}}$, then $\pgv{\tseq[\cs{p}]{\ty{\cpgvT{\Gamma}}}{\cpgvM{P}}{\tyunit}}$.
  \end{restatablelemma}
  \begin{restatabletheorem}{thmpcptopgvconfspreservation}[Preservation, ${\tm{\cpgvC{\cdot}}}$]
    \label{thm:pcp-to-pgv-confs-preservation}
    If $\pcp{\seq{P}{\ty{\Gamma}}}$, then $\pgv{\cseq[\child]{\ty{\cpgvT{\Gamma}}}{\cpgvC{P}}}$.
  \end{restatabletheorem}
\end{compacttheorems}

\subsubsection*{Operational correspondence}
Finally, we show that PCP and PGV are in operational correspondence along our translation. First, we link our two translations, and show that $\tm{\cpgvM{P}}$ \emph{must} reduce to $\tm{\cpgvC{P}}$, \ie $\tm{\cpgvC{\cdot}}$ is equivalent to translating with $\tm{\cpgvM{\cdot}}$ and performing several reduction steps:
\begin{compacttheorems}
  \begin{restatablelemma}{lempcptopgvcpgvMtocpgvC}
    \label{lem:pcp-to-pgv-cpgvM-to-cpgvC}
    For any $\pcp{\tm{P}}$, either:
    \begin{itemize}
    \item $\pgv{\tm{\child\;\cpgvM{P}}=\tm{\cpgvC{P}}}$; or
    \item   $\pgv{\tm{\child\;\cpgvM{P}}\cred^+\tm{\cpgvC{P}}}$, and for any $\pgv{\tm{\conf{C}}}$, if $\pgv{\tm{\child\;\cpgvM{P}}\cred\tm{\conf{C}}}$, then $\pgv{\tm{\conf{C}}\cred^\star\tm{\cpgvC{P}}}$.
    \end{itemize}
  \end{restatablelemma}
  \begin{proof}
    By induction on the structure of $\pcp{\tm{P}}$.
    Details in \cref{prf:lem-pcp-to-pgv-cpgvM-to-cpgvC}.
  \end{proof}
  \begin{restatabletheorem}{thmpcptopgvoperationalcorrespondencecompleteness}%
    [Operational Correspondence, Completeness, ${\tm{\cpgvC{\cdot}}}$]
    \label{thm:pcp-to-pgv-operational-correspondence-completeness}
    \hfill\\%newline before theorem statement
    If $\pcp{\seq{P}{\ty{\Gamma}}}$ and $\pcp{\tm{P}\red\tm{Q}}$,
    then $\pgv{\tm{\cpgvC{P}}\cred^+\tm{\cpgvC{Q}}}$.
  \end{restatabletheorem}
  \begin{proof}
    By induction on the derivation of $\pcp{\tm{P}\red\tm{Q}}$.
    We apply \cref{lem:pcp-to-pgv-cpgvM-to-cpgvC} for the cases in which
    the translation switches from $\tm{\cpgvC{\cdot}}$ to $\tm{\cpgvM{\cdot}}$,
    \ie under actions.
    We apply \cref{lem:pcp-to-pgv-confs-operational-correspondence-equiv} for
    \LabTirName{E-LiftSC}. 
    Details in \cref{prf:thm-pcp-to-pgv-operational-correspondence-completeness}.
  \end{proof}
  \begin{restatabletheorem}{thmpcptopgvoperationalcorrespondencesoundness}%
    [Operational Correspondence, Soundness, ${\tm{\cpgvC{\cdot}}}$]
    \label{thm:pcp-to-pgv-operational-correspondence-soundness}
    \hfill\\%newline before theorem statement
    If $\pcp{\seq{P}{\ty{\Gamma}}}$ and $\pgv{\tm{\cpgvC{P}}\cred\tm{\conf{C}}}$,
    there exists a $\tm{Q}$ such that $\pcp{\tm{P}\red^+\tm{Q}}$ and $\pgv{\tm{\conf{C}}\cred^\star\tm{\cpgvC{Q}}}$
  \end{restatabletheorem}
  \begin{proof}
    By induction on the derivation of $\pgv{\tm{\cpgvC{P}}\cred\tm{\conf{C}}}$.\simon{Surprising that you can get it by the derivation of the reduction relation---normally, 'soundness' would be proved by shunting into a canonical form and then proceeding by induction the structure of the term / induction on typing derivations.}
    Details in \cref{prf:thm-pcp-to-pgv-operational-correspondence-soundness}.
  \end{proof}
\end{compacttheorems}
